Validation of an Actuator Line Model Coupled to a Dynamic Stall Model for Pitching Motions Characteristic to Vertical Axis Turbines

### 2016-06-13 paper.tex
Wrapping and add space before citation

\section{Introduction}
Operating conditions of Vertical Axis Wind Turbines VAWTs are characterized as complex unsteady flows which
give a considerable challenge, both to describe using measurements and to
represent through simulation tools\cite{huyer1996unsteady}. Moreover, VAWT
blades are inherently exposed to cyclic variation in the angle of attack, which
gives cyclic blade forces and can give material fatigue damage. Accurate
modeling of the varying forces is therefore very important for the design of the
VAWT.

>>>>

\section{Introduction}

Operating conditions of Vertical Axis Wind Turbines VAWTs are characterized as
complex unsteady flows which give a considerable challenge, both to describe
using measurements and to represent through simulation
tools~\cite{huyer1996unsteady}. Moreover, VAWT blades are inherently exposed to
cyclic variation in the angle of attack, which gives cyclic blade forces and can
give material fatigue damage. Accurate modeling of the varying forces is
therefore very important for the design of the VAWT.
